|

### 2021-03-11 supplementary_information_science.Rmd
edits: si, table caption

**Table S3** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See Tables S1 and S2 for interpretation of the simulation parameters.

@@

**Table S4** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See Tables S1 and S2 for interpretation of the simulation parameters.

@@

**Table S5** List of fish species in Hokkaido, Japan, included in our statistical analysis. `r n_distinct(dat_hkd$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.

@@

**Table S6** List of fish species in the Midwest, US, included in our statistical analysis. `r n_distinct(dat_mw$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.

>>>>

**Table S3** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See **Tables S1 and S2** for interpretation of the simulation parameters.

@@

**Table S4** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See **Tables S1 and S2** for interpretation of the simulation parameters.

@@

**Table S5** List of fish species in Hokkaido, Japan, included in our statistical analysis. `r n_distinct(dat_hkd_site$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy of `r n_distinct(dat_hkd_site$SiteID)` sites.

@@

**Table S6** List of fish species in the Midwest, US, included in our statistical analysis. `r n_distinct(dat_mw_site$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy of `r n_distinct(dat_mw_site$SiteID)` sites.
